A Comparison of Graph Processing Systems

### 2020-08-20 documentation/paper/sections/overview/polymer.tex
kleine Änderungen

Polymer is very similar to Ligra, in fact Polymer inherits the programming interfaces \texttt{EdgeMap} and \texttt{VertexMap} from Ligra as its main interface.

Polymer is a vertex-centric framework, that tries to circumvent some of the random memory access drawbacks of such a design. It treats a NUMA machine as a distributed cluster and splits work and graph data accordingly between the nodes.\cite[p.187]{Polymer}
Application-defined data is not distributed. Other runtime state data is allocated in a distributed way but only accessed through a global lookup table.\cite[p.184]{Polymer}

>>>>

Polymer is very similar to Ligra, in fact Polymer inherits the programming interfaces \texttt{EdgeMap} and \texttt{VertexMap} from Ligra as its main interface.\cite{Polymer}

Polymer is a vertex-centric framework, that tries to circumvent some of the random memory access drawbacks of such a design. It treats a NUMA machine as a distributed cluster and splits work and graph data accordingly between the nodes.
Application-defined data is not distributed. Other runtime state data is allocated in a distributed way but only accessed through a global lookup table.

### 2020-08-20 documentation/paper/sections/testingMethods.tex
grouped bar plot, style for plots
kleine Änderungen

The complete log files and extracted raw results will be available in our repository as well.

@@

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PR in push and pull modes), we included the alternatives in our testing.

>>>>

The complete benchmark log files and extracted raw results will be available in our repository as well.

@@

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing.
